### 2023-01-11 paper.Rmd
load all packages in first chunk

```{r setup, include = FALSE}
library("papaja") # use the development version: `remotes::install_github("crsh/papaja@devel")`; currently 0.1.1.9001
library("anticlust")
library("knitr")
library("dplyr")
library("ggplot2")
library("tidyr")
# for formatting numbers in Rmarkdown, use my package prmisc (https://github.com/m-Py/prmisc)
library("prmisc") # remotes::install_github("m-Py/prmisc") 
options(digits = 2)
knitr::opts_chunk$set(message=FALSE, warning = FALSE, echo = FALSE, dev = "cairo_pdf")

>>>>

```{r setup, include = FALSE}
library(papaja) # use the development version: `remotes::install_github("crsh/papaja@devel")`; currently 0.1.1.9001
library(anticlust)
library(knitr)
library(dplyr)
library(ggplot2)
library(tidyr)
library(DescTools)
# for formatting numbers in Rmarkdown, use my package prmisc (https://github.com/m-Py/prmisc)
library(prmisc) # remotes::install_github("m-Py/prmisc") 
options(digits = 2)
knitr::opts_chunk$set(message=FALSE, warning = FALSE, echo = FALSE, dev = "cairo_pdf")
